Context Inconsistency Management \\in Pervasive Systems

### 2011-04-12 paper/paper.tex
rewrite introduction

\maketitle

In pervasive computing, contexts are used to make applications perform a certain action. Contexts can be seen as pieces of environmental information, which the applications depend on. Sometimes contexts are not consistent due to cross reads and misreads. The correctness of the contexts can be checked by evaluating the consistency constraints associated to them. There are multiple ways to check for consistency constraints. Constraint checking techniques are split up in two classes: Non-incremental checking and incremental checking. Incremental checking also consists of two classes: Entire Constraint Checking and Partial Constraint Checking. Once inconsistent contexts have been detected, an algorithm can be used to select the correct contexts. The algorithms use specific data structures, like ontology models, in order to resolve the inconsistencies. However, certain conflict resolving algorithms are too slow for use in practice. This paper describes a way to use an ontology model in combination with the Partial Constraint Checking algorithm in order to detect context inconsistencies fast enough, such that it can be used in practice. Another approach to handling context inconsistencies is representing them into the context model, as opposed to resolving them. This can be done efficiently by using fuzzy ontologies in a tree like structure, as we show in a use case.

>>>>

\maketitle
In pervasive computing applications use contexts to represent their changing environment and adapt their behavior to it. Due to environmental noises contexts can be imprecise or incorrect, resulting in context inconsistencies. These inconsistencies may set a pervasive application in a wrong state or misadjust its behavior. Therefore it is important to timely detect and resolve context inconsistencies.

In the next chapter we start with an overview of the existing solutions for handling context inconsistencies and argue why these solutions do not meet the requirements of pervasive applications. Next we present Partial Constraint Checking: an algorithm for constraint checking on huge sets of contexts that is far more efficient and effective than the existing approaches. In addition we discuss a Context Inconsistency Resolution algorithm that allows for resolving conflicting context sets without human intervention. Finally we propose a whole new approach to context inconsistencies: incorporating inconsistencies in to the context model by using fuzzy ontologies. We show that this approach makes conflict detection and resolution superfluous and has lots of potential for an efficient implementation using Partial Probability Calculation.
